\documentclass{article}
\usepackage{fullpage}
\title{CITC1310 - Programming I - Supplemental Syllabus}
\author{Dr. Robert Lowe - {\em relowe@pstcc.edu}}
\date{Fall 2019}

\begin{document}
\maketitle

\section{Grading}
\subsection*{Quizzes \& Exams: 40\% of Grade}
Weekly exams will be given. These will be given every Tuesday and will
consist of 10 multiple choice questions. Collectively, the quizzes are
worth 200 points.

There will be two exams, a midterm and a final.  The dates of these
exams are shown in bold in the course schedule.  Collectively, the
exams are worth 200 points.

\subsection*{Laboratory: 40\%}
Your grade from CITC1110 is 40\% of your grade in this class.

\subsection*{Class Participation: 20\%}
Attendance and class participation counts for 20\% of your grade in
this class.

\section{Schedule}
\section*{August 2019}
\begin{tabular}{rrrrrrr}
Su & Mo & Tu & We & Th & Fr & Sa\\
   &    &    &    &  1 &  2 &  3\\
 4 &  5 &  6 &  7 &  8 &  9 & 10\\
11 & 12 & 13 & 14 & 15 & 16 & 17\\
18 & 19 & 20 & 21 & 22 & 23 & 24\\
25 & 26 & 27 & 28 & 29 & 30 & 31\\
\end{tabular}

\begin{description}
    \item[August 26, 2019] - {\em PSTCC Classes Begin}
    \item[August 27, August 29] - Week 1 - Introduction to Java Programming and Algorithms
        \newline Chapter 1
\end{description}

\hrulefill

\section*{September 2019}
\begin{tabular}{rrrrrrr}
Su & Mo & Tu & We & Th & Fr & Sa\\
 1 &  2 &  3 &  4 &  5 &  6 & 7\\
 8 &  9 & 10 & 11 & 12 & 13 & 14\\
15 & 16 & 17 & 18 & 19 & 20 & 21\\
22 & 23 & 24 & 25 & 26 & 27 & 28\\
29 & 30 &    &    &    &    &   \\
\end{tabular}

\begin{description}
    \item[September 2, 2019] - {\em Holiday - Labor Day - College Closed}
    \item[September 3, September 5] - Week 2 - Software Development
        Environment-Creating; Compiling; Executing a Java Program
        \newline Chapter 1
    \item[September 10, September 12] - Week 3 - Data Types Variables,
        Operations; Software Development Process/Programming Style,
        Documentation
        \newline Chapter 2
    \item[September 17, September 19] - Week 4 - Selection Algorithms;
        Conditional Statements; Switch statements
        \newline Chapter 3
    \item[September 24, September 26] - Week 5 - Mathematical
        Functions, Formatting Output, Use the Java API
        \newline Chapter 4
\end{description}

\hrulefill

\section*{October 2019}
\begin{tabular}{rrrrrrr}
Su & Mo & Tu & We & Th & Fr & Sa\\
   &    &  1 &  2 &  3 &  4 &  5\\
 6 &  7 &  8 &  9 & {\bf 10} & 11 & 12\\
13 & 14 & 15 & 16 & 17 & 18 & 19\\ 
20 & 21 & 22 & 23 & 24 & 25 & 26\\ 
27 & 28 & 29 & 30 & 31 &    &   \\
\end{tabular}

\begin{description}
    \item[October 1, October 3] - Week 6 - Characters, String;
        \newline Chapter 4
    \item[October 8] - Week 7 - Repetition Statements and
        Algorithms; while/do-while/for loops;
        \newline Chapter 5
    \item[October 10] - Midterm Exam
    \item[October 15, October 17] - Week 8 - Methods; Defining and
        Calling a Method; Passing Parameters by Values
        \newline Chapter 6
    \item[October 22, October 24] - Week 9 - Overloading Methods; The
        Scope of Variables
        \newline Chapter 6
    \item[October 29, October 31] - Week 10 - Objects and Classes;
        Constructors; Accessing Objects via Reference variables
        \newline Chapter 9
\end{description}

\hrulefill

\section*{November 2019}
\begin{tabular}{rrrrrrr}
Su & Mo & Tu & We & Th & Fr & Sa\\
   &    &    &    &    &  1 &  2\\
 3 &  4 &  5 &  6 &  7 &  8 &  9\\
10 & 11 & 12 & 13 & 14 & 15 & 16\\
17 & 18 & 19 & 20 & 21 & 22 & 23\\
24 & 25 & 26 & 27 & 28 & 29 & 30\\
\end{tabular}

\begin{description}
    \item[November 5, November 7] - Week 11 - Static Variables;
        Visibility Modifiers; OOD; UML Class Diagram; Accessors/Mutators
        Encapsulation
        \newline Chapter 9
    \item[November 12, November 14] - Week 12 - Passing Objects to
        Methods; The this reference; Class Abstraction and Encapsulation
        \newline Chapter 9
    \item[November 19, November 21] - Week 13 - Array Basics;
        Single-Dimensional Arrays
        \newline Chapter 7
    \item[November 26] - Week 14 - Single-Dimensional Arrays Continued
        \newline Chapter 7
    \item[November 27 - December 1] {\em Thanksgiving Break - College Closed}
\end{description}

\hrulefill

\section*{December 2019}
\begin{tabular}{rrrrrrr}
Su & Mo & Tu & We & Th & Fr & Sa\\
 1 &  2 &  3 &  4 &  5 &  6 &  7\\
 8 &  9 & 10 & 11 & {\bf 12} & 13 & 14\\
15 & 16 & 17 & 18 & 19 & 20 & 21\\
22 & 23 & 24 & 25 & 26 & 27 & 28\\
29 & 30 & 31 &    &    &    &   \\
\end{tabular}

\begin{description}
    \item[December 3, December 5] - Week 15 - Review
    \item[December 12 6:30PM] - Final Exam
\end{description}

\hrulefill

\section{Suicide Prevention Counseling}
Pellissippi State Community College is committed to and cares about
all students. If you or someone you know at Pellissippi State feels
overwhelmed, hopeless, depressed, and/or is thinking about dying by
suicide, supportive services are available. The National Suicide
Prevention Lifeline at 1-800-273-TALK (8255) provides access to
trained telephone counselors, 24 hours a day, 7 days a week or the
Crisis Text Line by texting ``TN'' to 741741. Veterans may also wish
to contact the Veterans Crisis Line at 1-800-273-8255 (press 1) or
Text 838255. Counseling is available to Pellissippi State students at
all campuses.

\end{document}
